\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-01-30 paper/main.tex
minor updates

The aim of \name is to predict candidate drugs that target a given
protein; the challenge is to develop a training and evaluation scheme
that does not simply overfit to the inherent biases in training and
testing data.

In general, when concerning cross-validation splitting schemes for DTI prediction, there are the following three options:
\begin{enumerate}
	\item Build split over drugs
	\item Build split over drug-target pairs
	\item Build split over proteins
\end{enumerate}
where the first and third option concern splitting drugs and proteins, respectively, into train, validation and test sets, and arranging the corresponding drug-target interactions. Hereby, different training and prediction schemes lead to divergent expressiveness of the resulting model. \\
The most common scheme for DTI prediction is the split over drug-target pairs \citep{Survey2018}, where likely all drugs and targets of the validation and testing phase have already occurred in the training phase, as part of other drug-target pairs. Thus, the first and second splitting scheme are exposed to the first dataset bias and are hence more likely vulnerable to transductive inference by just predicting recently seen structures, rather than implementing inductive inference and generalizing over the drug representations. Second, these two strategies are more susceptible to the second and third bias, as only in these cases the model may overfit on the number of existing interactions, while in the third scheme the number of interactions of the test proteins is not known. \\

Considering the publications of the last

>>>>

\todo[inline]{Likely discussion:}
The aim of \name is to predict candidate drugs that target a given
protein; the challenge is to develop a training and evaluation scheme
that does not simply overfit to the inherent biases in training and
testing data.
In general, when performing cross-validation for DTI prediction, the
options are to split over drug--target pairs, split over drugs, and
split over proteins; the last two options ensure that at least parts
of the interactions are not seen during training and evaluate either
how well targets are predicted for unseen drugs or unseen proteins.

\todo[inline]{Likely discussion:}
The most common scheme for DTI prediction is the split over
drug--target pairs \citep{Survey2018}, where likely all drugs and
targets of the validation and testing phase have already occurred in
the training phase, as part of other drug-target pairs. Thus, the
first and second splitting scheme are exposed to the first dataset
bias and are hence more likely vulnerable to transductive inference by
just predicting recently seen structures, rather than implementing
inductive inference and generalizing over the drug
representations. Second, these two strategies are more susceptible to
the second and third bias, as only in these cases the model may
overfit on the number of existing interactions, while in the third
scheme the number of interactions of the test proteins is not known.
